SafeNet: A European database of plant-pollinator interactions

### 2024-03-27 Manuscript/4_Figure_4.Rmd
edits

---
output: pdf_document
---

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, out.width="95%", fig.cap= "\\textbf{Figure 3}.", fig.width=8, fig.height=8}

>>>>

---
output:
  pdf_document:
header-includes:
- \usepackage{caption}
- \captionsetup[figure]{labelformat=empty}
- \captionsetup[table]{labelformat=empty}
---

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, out.width="95%", fig.cap= "\\textbf{Figure 4}.", fig.width=8, fig.height=8}

### 2024-03-27 Manuscript/5_Figure_5.Rmd
edits

---
output: pdf_document
---

@@

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, out.width="95%", fig.cap= "\\textbf{Figure 2}. Proportion of the major pollinator orders by habitat types and bioclimatic regions in the SafeNet database. The orders, from left to right, include Hymenoptera, Diptera, Lepidoptera and Coleoptera. The horizontal barplot on the right indicates the number of studies that were conducted on each habitat type or bioclimatic region. Note that a single study can countribute to more than one habitat or bioclimatic region. Areas with a greater number of studies are more likely to depict accurate proportions of pollinators in those systems.", fig.width=4.5, fig.height=8, fig.align='center'}

#Read interaction data 
data = readRDS("../Data/3_Final_data/Interactions_uncounted.rds")
#Load data (done it in earlier chunks)
#Select cols of interest
data1 = data %>% 
select(Study_id, Network_id, Authors_habitat,
  Corine_land_cover, SafeNet_habitat, Bioregion,
  Latitude, Longitude, Day, Month, Year, Plant_rank,
  Plant_status, Plant_matchtype, Plant_accepted_name,Plant_order,
  Pollinator_rank, Pollinator_status, Pollinator_matchtype,
  Pollinator_accepted_name, Pollinator_order, Interaction)

@@

#c("azure3","steelblue", "wheat2", "tomato3")

>>>>

---
output:
  pdf_document:
header-includes:
- \usepackage{caption}
- \captionsetup[figure]{labelformat=empty}
- \captionsetup[table]{labelformat=empty}
---

@@

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, out.width="95%", fig.cap= "\\textbf{Figure 5}. Proportion of the major pollinator orders by habitat types and bioclimatic regions in the SafeNet database. The orders, from left to right, include Hymenoptera, Diptera, Lepidoptera and Coleoptera. The horizontal barplot on the right indicates the number of studies that were conducted on each habitat type or bioclimatic region. Note that a single study can countribute to more than one habitat or bioclimatic region. Areas with a greater number of studies are more likely to depict accurate proportions of pollinators in those systems.", fig.width=4.5, fig.height=8, fig.align='center'}

#Read interaction data 
data = readRDS("../Data/3_Final_data/Interactions_uncounted.rds")

data = data %>%
dplyr::mutate(Year = lubridate::year(Date), 
                Month = lubridate::month(Date), 
                Day = lubridate::day(Date))

#Load data (done it in earlier chunks)
#Select cols of interest
data1 = data %>% 
select(Study_id, Network_id, Authors_habitat,
  SafeNet_habitat, Bioregion,
  Latitude, Longitude, Day, Month, Year, Plant_rank,
  Plant_status, Plant_matchtype, Plant_accepted_name,Plant_order,
  Pollinator_rank, Pollinator_status, Pollinator_matchtype,
  Pollinator_accepted_name, Pollinator_order, Interaction)

@@

### 2024-03-27 Manuscript/Ms.qmd
edits

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE}
#Load data
data = readRDS("../Data/3_Final_data/Interactions_uncounted.rds")
#Bee-syrphid Masterlist
master_list = read_csv("../Data/Species_taxonomy/Thesaurus/Master_bees_syrphids.csv")
#Load butterfly masterlist
master_list1 <- read.delim(file = "../Data/Species_taxonomy/Thesaurus/Butterfly_taxon.txt",
                    header = T)
#Prepare table with data structure (as it would be made available to others)
safenet_database = readRDS("../Data/3_Final_data/Interaction_data.rds")

@@

@@

@@

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, out.width="95%", fig.width=10, fig.height=10, fig.cap= "\\textbf{Figure 2}. Phylogenetic representation of bee genera in the SafeNet database within the context of all European bee genera. The number of interactions recorded per genus in the database is illustrated using circles, with their sizes proportional to the number of interactions on a logarithmic scale. Additionally, a gradient of colors ranging from yellow to dark purple aids in this visualization. The coverage of species recorded in SafeNet per genus at the European level is depicted with orange and light grey bars, representing the percentage of species included and not included in the database, respectively, out of the total number of bee species per genus at the European level. Grey bars indicate the total number of species per genus at the European level."}

@@

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, out.width="95%", fig.cap= "\\textbf{Figure 3}. Phylogenetic representation of the plant families in the SafeNet database within the context of all flowering plant families occurring in Europe. The number of interactions recorded per genus in the database is illustrated using circles, with their sizes proportional to the number of interactions on a logarithmic scale. Additionally, a gradient of colors ranging from yellow to dark purple aids in this visualization. The coverage of species recorded in SafeNet per genus at the European level is depicted with orange and light grey bars, representing the percentage of species included and not included in the database, respectively, out of the total number of flowering plant species per family at the European level. Grey bars indicate the total number of species per family at the European level on logarithmic scale.", fig.width=8, fig.height=8}

@@

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, out.width="95%", fig.cap= "\\textbf{Figure 4}. Proportion of the major pollinator orders by habitat types and bioclimatic regions in the SafeNet database. The orders, from left to right, include Hymenoptera, Diptera, Lepidoptera and Coleoptera. The horizontal barplot on the right indicates the number of studies that were conducted on each habitat type or bioclimatic region. Note that a single study can countribute to more than one habitat or bioclimatic region. Areas with a greater number of studies are more likely to depict accurate proportions of the different pollinator orders in those systems.", fig.width=4.5, fig.height=8, fig.align='center'}

#Load data (done it in earlier chunks)
#Select cols of interest
data1 = data %>% 
select(Study_id, Network_id, Authors_habitat,
  SafeNet_habitat, Bioregion,
  Latitude, Longitude, Day, Month, Year, Plant_rank,
  Plant_status, Plant_matchtype, Plant_accepted_name,Plant_order,
  Pollinator_rank, Pollinator_status, Pollinator_matchtype,
  Pollinator_accepted_name, Pollinator_order, Interaction)

@@

#Check number of studies by habitat
habitat = data %>% 
select(Study_id, SafeNet_habitat) %>% 
distinct() %>%  
group_by(SafeNet_habitat) %>% 
summarise(Habitat_count = n()) 
#Check number of studies by bioregion
bioregion = data %>% 
select(Study_id, Bioregion) %>% 
distinct() %>%  
group_by(Bioregion) %>% 
summarise(Bioregion_count = n()) 
#Check pols by habitat
pollinator_percent = data1 %>%
group_by(SafeNet_habitat, Pollinator_order) %>%
filter(Pollinator_accepted_name!= "Apis mellifera") %>% 
filter(Pollinator_order %in% main_orders) %>% 
summarise(count = n()) %>%
group_by(SafeNet_habitat) %>%
mutate(Proportion = count/sum(count)) %>%
select(-count) 
#Check pols by bioregion
pollinator_percent_bio = data1 %>%
group_by(Bioregion, Pollinator_order) %>%
filter(Pollinator_accepted_name!= "Apis mellifera") %>% 
filter(Pollinator_order %in% main_orders) %>% 
summarise(count = n()) %>%
group_by(Bioregion) %>%
mutate(Proportion = count/sum(count)) %>%
select(-count) 
#Preparing datasets for horizontal plot
a1 = habitat %>% 
mutate(Group = "Habitat") %>% 
rename(Habitat = SafeNet_habitat) %>% 
rename(Count = Habitat_count)

>>>>

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE}

#Read data
data = readRDS("../Data/3_Final_data/Interactions_uncounted.rds")%>% 
mutate(Network_id = paste0(Study_id, Network_id))  
#Bee-syrphid Masterlist
master_list = read_csv("../Data/Species_taxonomy/Thesaurus/Master_bees_syrphids.csv")
#Load butterfly masterlist
master_list1 <- read.delim(file = "../Data/Species_taxonomy/Thesaurus/Butterfly_taxon.txt",
                    header = T)
#Prepare table with data structure (as it would be made available to others)
safenet_database = readRDS("../Data/3_Final_data/Interaction_data.rds")

@@

## Sampling coverage

bootstraping, inext package

@@

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, out.width="95%", fig.cap= "\\textbf{Figure 2}. Graphs (a-b-c) indicate the accumulation curves for pollinators, plants, and their interactions across sampling sites. Grey solid lines represent 100 randomized accumulation curves, the black solid lines represents the interpolated curve (i.e., the mean across curves), and the red dashed lines illustrates the extrapolated curve for approximately 3000 sampling sites. The solid black points indicate the number of species and interactions contained in the database. Graphs (d-e) indicate the percentage of occurrence (i.e., incidence) of plant and pollinator species across sampling sites. Species on the left (i.e., common) are found in many sampling sites, while species on the right (i.e., rare) are found in few or only a single sampling site. Graph (f) shows the accumulation curve of pollinator species across increasing number of plant species. This last graph uses the same color and shape structure as the ones in the top panel.", fig.width=10, fig.height=6, out.width="115%"}

#Pollinators-----
poll_output = readRDS("../Data/Working_files/pollinator_sampling_coverage.rds")
pollinators_curves = readRDS("../Data/Working_files/collectors_curves_pollinators.rds")
#Create dataset
d_poll = poll_output$iNextEst$Network_id
#Check cols
d_poll$col = d_poll$method

#Now create tibble with same structure
a_poll = tibble(t = pollinators_curves$Study_sampled, 
           method = as.character(pollinators_curves$iteration), 
           qD = pollinators_curves$Unique_spp_cumulative,
           col = "collectors")

#Bind datasets 
d_poll1 = bind_rows(d_poll, a_poll)
d_poll1_point = d_poll1 %>%  filter(method == "observed")
d_poll1_lines = d_poll1 %>%  filter(!method == "observed")

#Order levels
d_poll1_lines$col = factor(d_poll1_lines$col, levels = c("collectors", "interpolated", "extrapolated"))
#Plot
p1 = ggplot(d_poll1_lines, aes(x = t, y = qD, group = method, color = col)) +
geom_line(aes(linetype = col),size = 0.65) +
scale_colour_manual(values = c("gray", "black", "red"), labels = c("Randomizations", "Interpolated", "Extrapolated")) +
scale_linetype_manual(values = c("solid", "solid", "dashed"),  labels = c("Randomizations", "Interpolated", "Extrapolated")) + 
geom_ribbon(aes(ymin = qD.LCL, 
    ymax=qD.UCL, fill = col),alpha=0.2, colour = NA, show.legend = FALSE)+
scale_fill_manual(values = c("gray", "black", "red")) +
geom_point(data = d_poll1_point, col = "black", size=2) + 
ylab("Pollinator species") +
xlab("Sampling sites") +
theme_bw() +
coord_cartesian(expand = FALSE, clip = "off")  +
xlim(0,3000)+
ylim(0, 3000) +
ggtitle("(a)") +
theme(plot.margin = margin(r = 12))

#Plants-----
plant_output = readRDS("../Data/Working_files/plant_sampling_coverage.rds")
plant_curves = readRDS("../Data/Working_files/collectors_curves_plants.rds")
#Create dataset
d_plant = plant_output$iNextEst$Network_id
#Check cols
d_plant$col = d_plant$method

#Now create tibble with same structure
a_plant = tibble(t = plant_curves$Study_sampled, 
           method = as.character(plant_curves$iteration), 
           qD = plant_curves$Unique_spp_cumulative,
           col = "collectors")

#Bind datasets 
d_plant1 = bind_rows(d_plant, a_plant)
d_plant1_point = d_plant1 %>%  filter(method == "observed")
d_plant1_lines = d_plant1 %>%  filter(!method == "observed")

#Order levels
d_plant1_lines$col = factor(d_plant1_lines$col, levels = c("collectors", "interpolated", "extrapolated"))
#Plot
p2 = ggplot(d_plant1_lines, aes(x = t, y = qD, group = method, color = col)) +
geom_line(aes(linetype = col), size = 0.65) +
scale_colour_manual(values = c("gray", "black", "red"), labels = c("Randomizations", "Interpolated", "Extrapolated")) +
scale_linetype_manual(values = c("solid", "solid", "dashed"),  labels = c("Randomizations", "Interpolated", "Extrapolated")) + 
geom_ribbon(aes(ymin = qD.LCL, 
    ymax=qD.UCL, fill = col),alpha=0.2, colour = NA, show.legend = FALSE)+
scale_fill_manual(values = c("gray", "black", "red")) +
geom_point(data = d_plant1_point, col = "black", size=2) + 
ylab("Plant species") +
xlab("Sampling sites") +
theme_bw() +
coord_cartesian(expand = FALSE, clip = "off")  +
xlim(0,3000)+
ylim(0, 3000)+
ggtitle("(b)")+
theme(plot.margin = margin(r = 12))

#Interactions-----
int_output = readRDS("../Data/Working_files/interactions_sampling_coverage.rds")
interactions_curves = readRDS("../Data/Working_files/collectors_curves_interactions.rds")
#Create dataset
d_int = int_output$iNextEst$Network_id
#Check cols
d_int$col = d_int$method

#Now create tibble with same structure
a_poll = tibble(t = interactions_curves$Study_sampled, 
           method = as.character(interactions_curves$iteration), 
           qD = interactions_curves$Unique_spp_cumulative,
           col = "collectors")

#Bind datasets 
d_int1 = bind_rows(d_int, a_poll)
d_int1_point = d_int1 %>%  filter(method == "observed")
d_int1_lines = d_int1 %>%  filter(!method == "observed")

#Plot
#Order levels
d_int1_lines$col = factor(d_int1_lines$col, levels = c("collectors", "interpolated", "extrapolated"))
#Plot
p3 = ggplot(d_int1_lines, aes(x = t, y = qD, group = method, color = col)) +
geom_line(aes(linetype = col), size = 0.65) +
scale_colour_manual(values = c("gray", "black", "red"), labels = c("Randomizations", "Interpolated", "Extrapolated")) +
scale_linetype_manual(values = c("solid", "solid", "dashed"),  labels = c("Randomizations", "Interpolated", "Extrapolated")) + 
geom_ribbon(aes(ymin = qD.LCL, 
    ymax=qD.UCL, fill = col),alpha=0.2, colour = NA, show.legend = FALSE)+
scale_fill_manual(values = c("gray", "black", "red")) +
geom_point(data = d_int1_point, col = "black", size=2) + 
ylab("Interactions") +
xlab("Sampling sites") +
theme_bw() +
coord_cartesian(expand = FALSE, clip = "off")  +
xlim(0,3000) +
ylim(0, 30000)+
ggtitle("(c)")

#----------------#
#Pollinators
#----------------#
#Read data
data = readRDS("../Data/3_Final_data/Interactions_uncounted.rds")%>% 
mutate(Network_id = paste0(Study_id, Network_id))  
#First select cols of rank, accepted name and study ID
#Then select unique levels by study ID
#Now sum levels (maximum can be as maximum number of studies)
poll_spread = data %>% 
select(Pollinator_rank, Pollinator_accepted_name, Network_id) %>% 
group_by(Network_id) %>% 
filter(Pollinator_rank == "SPECIES") %>% 
distinct(Pollinator_accepted_name) %>% 
ungroup() %>% 
count(Pollinator_accepted_name) %>% 
rename(n_networks_shared = n) %>% 
arrange(-n_networks_shared) %>% 
mutate(Percent_total = n_networks_shared / n_distinct(data$Network_id))

#Obtain most common pollinator for plotting
most_common_poll = poll_spread %>% filter(n_networks_shared == max(n_networks_shared)) %>%
select(Pollinator_accepted_name) %>% pull()

#Plot
o1 = ggplot(poll_spread, 
aes(reorder(Pollinator_accepted_name,-Percent_total), Percent_total)) +
geom_bar(stat = "identity", 
           color = "#D55E00",
           lwd = 0.03, fill = "#D55E00") +
ylab("Shared pollinators (%)") +
theme_minimal()+
theme(axis.text.x = element_blank(),
  axis.ticks.x=element_blank(),
  axis.ticks.y = element_line(size = 0.2),
  panel.grid.major.x = element_blank(),
  panel.grid.minor.y = element_blank(),
  panel.grid.major.y = element_line(size=0.2, linetype = 2)) +
xlab("Pollinator species") +
ylab("Occurrence across sampling sites") + 
geom_vline(xintercept = quantile_50, linetype="dashed", 
color = "black", size=0.35) + 
annotate(geom="text", x=1450, y=0.60, label="50th percentile",color="black", size = 3) +
annotate(geom="text", x=140, y=0.67, label=most_common_poll[1],color="black",  fontface = 'italic', size = 3)+
annotate(geom="text", x=200, y=-0.05, label="Common spp."
      ,color="black",  size = 3) +
annotate(geom="text", x=1800, y=-0.05, label="\'Rare\' spp."
      ,color="black",  size = 3)  +
scale_y_continuous(breaks = seq(0, 0.7, by= 0.25), expand = c(0, 0)) + 
coord_cartesian(xlim=c(0, nlevels(factor(poll_spread$Pollinator_accepted_name))),
                ylim=c(0,0.7), clip="off") +
ggtitle("(d)")

#----------------#
#Plants
#----------------#
plant_spread = data %>% 
select(Plant_rank, Network_id, Plant_accepted_name) %>% 
group_by(Network_id) %>% 
filter(Plant_rank == "SPECIES") %>% 
distinct(Plant_accepted_name) %>% 
ungroup() %>% 
count(Plant_accepted_name) %>% 
rename(n_networks_shared = n) %>% 
arrange(-n_networks_shared) %>% 
mutate(Percent_total = n_networks_shared / n_distinct(data$Network_id))

#Seelect quantile 50% from the total number of species
spp_number = plant_spread %>%  
select(Plant_accepted_name) %>% 
n_distinct()
df = seq(1, spp_number)
quantile_50 = quantile(df, 0.5)

#Obtain most common plant for plotting
most_common_plant = plant_spread %>% filter(n_networks_shared == max(n_networks_shared)) %>%
select(Plant_accepted_name) %>% pull()

o2 = ggplot(plant_spread, 
aes(reorder(Plant_accepted_name,-Percent_total), Percent_total, fill = Plant_accepted_name)) +
geom_bar(stat = "identity", 
           color = "#009E73",
           lwd = 0.03, fill = "#009E73") +
theme_minimal()+
theme(axis.text.x = element_blank(),
         axis.ticks.x=element_blank(),
         axis.ticks.y = element_line(size = 0.2),
         panel.grid.major.x = element_blank(),
         panel.grid.minor.y = element_blank(),
         panel.grid.major.y = element_line(size=0.2, linetype =  2)) +
xlab("Plant species") +
ylab("Occurrence across sampling sites") + 
geom_vline(xintercept = quantile_50, linetype="dashed", 
          color = "black", size=0.35) + 
annotate(geom="text", x=950, y=0.60, label="50th percentile",color="black", size = 3) + 
annotate(geom="text", x=100, y=0.4, label=most_common_plant[1]
      ,color="black",  fontface = 'italic', size = 3)+
annotate(geom="text", x=150, y=-0.05, label="Common spp."
      ,color="black",  size = 3) +
annotate(geom="text", x=1200, y=-0.05, label="\'Rare\' spp."
      ,color="black",  size = 3) + 
scale_y_continuous(breaks = seq(0, 0.7, by= 0.25), expand = c(0, 0), labels = label_number(accuracy = 0.01)) +
coord_cartesian(xlim=c(0, nlevels(factor(plant_spread$Plant_accepted_name))),
                ylim=c(0, 0.7), clip="off") +
ggtitle("(e)")

plant_poll = readRDS("../Data/Working_files/collectors_curves_plant_ploll.rds")
rarefaction_curve1 = readRDS("../Data/Working_files/rarefaction_curve_plant_poll.rds")

#Plot curves
pp1 = plant_poll %>% 
ggplot(aes(x = Plant_sampled, y= Unique_spp_cumulative, group = iteration)) +
geom_line(color = "gray") +
geom_smooth(data = rarefaction_curve1, 
  aes(x = Plant_sampled, y = mean_curve), inherit.aes = FALSE,method = "loess", color = "black", size = 0.65, linetype = "solid", se = FALSE, span = 0.5) +  
geom_point(data = rarefaction_curve1, x = max(rarefaction_curve1$Plant_sampled), y = max(rarefaction_curve1$mean_curve), inherit.aes = FALSE, size=2) +
ylab("Pollinator species") +
xlab("Plant species") +
theme_bw() +
coord_cartesian(expand = FALSE, clip = "off") +
ggtitle("(f)") +
scale_x_continuous(breaks = seq(0, 1400, by = 400), limits=c(0,1400)) +
ylim(0,2500)

#Plot all
a = p1 + p2 + p3 + plot_layout(guides = "collect") & theme(legend.title=element_blank(),
      axis.title = element_text(size=12, face = "bold"),
      axis.text = element_text(size=10),
      plot.title = element_text(size=18))
b = o1 + o2 + pp1 & 
  theme(axis.title = element_text(size=12, face = "bold"),
        axis.text = element_text(size=10),
      plot.title = element_text(size=18))

a/b

@@

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, out.width="95%", fig.width=10, fig.height=10, fig.cap= "\\textbf{Figure 3}. Phylogenetic representation of bee genera in the SafeNet database within the context of all European bee genera. The number of interactions recorded per genus in the database is illustrated using circles, with their sizes proportional to the number of interactions on a logarithmic scale. Additionally, a gradient of colors ranging from yellow to dark purple aids in this visualization. The coverage of species recorded in SafeNet per genus at the European level is depicted with orange and light grey bars, representing the percentage of species included and not included in the database, respectively, out of the total number of bee species per genus at the European level. Grey bars indicate the total number of species per genus at the European level."}

@@

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, out.width="95%", fig.cap= "\\textbf{Figure 4}. Phylogenetic representation of the plant families in the SafeNet database within the context of all flowering plant families occurring in Europe. The number of interactions recorded per genus in the database is illustrated using circles, with their sizes proportional to the number of interactions on a logarithmic scale. Additionally, a gradient of colors ranging from yellow to dark purple aids in this visualization. The coverage of species recorded in SafeNet per genus at the European level is depicted with orange and light grey bars, representing the percentage of species included and not included in the database, respectively, out of the total number of flowering plant species per family at the European level. Grey bars indicate the total number of species per family at the European level on logarithmic scale.", fig.width=8, fig.height=8}

@@

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, out.width="95%", fig.cap= "\\textbf{Figure 5}. Proportion of the major pollinator orders by habitat types and bioclimatic regions in the SafeNet database. The orders, from left to right, include Hymenoptera, Diptera, Lepidoptera and Coleoptera. The horizontal barplot on the right indicates the number of studies that were conducted on each habitat type or bioclimatic region. Note that a single study can countribute to more than one habitat or bioclimatic region. Areas with a greater number of studies are more likely to depict accurate proportions of the different pollinator orders in those systems.", fig.width=4.5, fig.height=8, fig.align='center'}

@@

#Check number of studies by habitat
habitat = data %>% 
select(Study_id, SafeNet_habitat) %>% 
distinct() %>%  
group_by(SafeNet_habitat) %>% 
summarise(Habitat_count = n()) 
#Check number of studies by bioregion
bioregion = data %>% 
select(Study_id, Bioregion) %>% 
distinct() %>%  
group_by(Bioregion) %>% 
summarise(Bioregion_count = n()) 
#Check pols by habitat
pollinator_percent = data %>%
group_by(SafeNet_habitat, Pollinator_order) %>%
filter(Pollinator_accepted_name!= "Apis mellifera") %>% 
filter(Pollinator_order %in% main_orders) %>% 
summarise(count = n()) %>%
group_by(SafeNet_habitat) %>%
mutate(Proportion = count/sum(count)) %>%
select(-count) 
#Check pols by bioregion
pollinator_percent_bio = data %>%
group_by(Bioregion, Pollinator_order) %>%
filter(Pollinator_accepted_name!= "Apis mellifera") %>% 
filter(Pollinator_order %in% main_orders) %>% 
summarise(count = n()) %>%
group_by(Bioregion) %>%
mutate(Proportion = count/sum(count)) %>%
select(-count) 
#Preparing datasets for horizontal plot
a1 = habitat %>% 
mutate(Group = "Habitat") %>% 
rename(Habitat = SafeNet_habitat) %>% 
rename(Count = Habitat_count)
